Temporal stability in human interaction networks: sector sizes, topological prominence and time activity

### 2015-10-04 paper.tex
terminada passada

\section{Conclusions}\label{sec:conc}
The most important result from the analysis of time evolution of the four email lists is certainly the time-independence observed not only for the activity but also for the properties of the networks themselves.
For example, the relative fractions of participants classified as hubs, intermediary and peripheral vertices remained practically constant along time across all email lists studied.
Furthermore, the PCA analysis of the topological metrics characterizing the networks also indicated that the contribution of each metric did not vary in time.
Centrality metrics were found to be the most relevant to characterize the network topology, followed by symmetry-related metrics, which were more relevant, with respect to variance, than clustering.

A systematic study of the activity of participants belonging to the three distinct Erd\"os sectors indicated simple patterns for hubs and peripheral vertices, while the network structure was governed by the intermediary vertices. These properties were shared by all email lists and were time-independent, being consistent with the literature. Moreover, both the distribution of Erd\"os sectors and the contribution from the metrics to the PCA were found to apply to networks from Facebook, Twitter and Participabr. We may therefore consider the classification of agents into Erd\"os sectors as a first step leading to a human typology which bridges exact sciences, with quantitative procedures for the classification, and human sciences, where there is a legacy in the observation of human types.

>>>>

\section{Conclusions}\label{sec:conc}
The most important result from the analysis of temporal evolution of the four email lists is certainly the time-independence observed not only for the activity but also for the properties of the networks themselves.
For example, the relative fractions of participants classified as hubs, intermediary and peripheral vertices remained practically constant along time across all email lists studied.
Furthermore, the PCA analysis of the topological metrics characterizing the networks also indicated that the contribution of each metric did not vary.
Centrality metrics were found to be the most relevant to characterize the network topology, followed by symmetry-related metrics, which were more relevant, with respect to variance, than clustering coefficient.

A systematic study of the activity of participants belonging to the three distinct Erd\"os sectors indicated simple patterns for hubs and peripheral vertices, while the network structure was governed by the intermediary vertices. These properties were shared by all email lists and were time-independent, which is consistent with the literature.
Moreover, both the distribution of participants in the Erd\"os sectors and the contribution of the metrics to the principal components were found the same in networks from Facebook, Twitter and Participabr.
We may therefore consider the Erd\"os sectors as leading to a human typology which bridges exact sciences, with quantitative procedures for the classification, and human sciences, where there is a legacy in the observation of human types.
